Standartox

### 2019-09-27 README.Rmd
changes

- [standartox-build](https://github.com/andschar/standartox-build) - Compiles the tool
- [standartox-app](https://github.com/andschar/standartox-build) - Serves the website and API
- [standartox](https://github.com/andschar/standartox) - R-package

>>>>

- [standartox-build](https://github.com/andschar/standartox-build) - Compiles the tool
- [standartox-app](https://github.com/andschar/standartox-app) - Serves the website and API
- [standartox](https://github.com/andschar/standartox) - R-package
